Double White Dwarf Mergers with CASTRO\\ I. Methodology and Code Validation

### 2012-12-05 paper.tex
document gravity correction

@@

>>>>

We also modify slightly the correction done to the gravitational
source terms after integrating the system in time.  In the original
Castro paper (Eqs. 19 and 20), the state after the conservative update
due to fluxes and external sources (other than gravity) was
represented with the superscript `$(2,\star)$'.  The gravitational
sources were then corrected, making them centered in time, yielding
the final state at the end of the hydrodynamics step, indicated with
the superscript `$(2)$'.  This appeared as:
\begin{eqnarray}
(\rho {\bf u})^{(2)} &=& (\rho {\bf u})^{(2,\star)} +
   \frac{\Delta t}{2} \left [ (\rho {\bf g})^{(2,\star)} - 
                              (\rho {\bf g})^{(1)} \right ]\\
(\rho E)^{(2)} &=& (\rho E)^{(2,\star)} +
   \frac{\Delta t}{2} \left [ (\rho {\bf u\cdot g})^{(2,\star)} - 
                              (\rho {\bf u\cdot g})^{(1)} \right ]
\end{eqnarray}
Here we make the subtle change of using the corrected ${\bf u}$ in the
correction to the energy.  So our new energy correction equation appears as:
\begin{equation}
(\rho E)^{(2)} = (\rho E)^{(2,\star)} +
   \frac{\Delta t}{2} \left [ (\rho {\bf u\cdot g})^{(2)} - 
                              (\rho {\bf u\cdot g})^{(1)} \right ]
\end{equation}
Both of these are second-order accurate, but we've found that the latter
is slightly better for conserving energy.

@@

rotation
